‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēó‚Ėą‚Ėą‚ēó ‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēó ‚Ėą‚Ėą‚ēó   ‚Ėą‚Ėą‚ēó‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēó ‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēó    ‚Ėą‚Ėą‚ēó  ‚Ėą‚Ėą‚ēó‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēó
‚Ėą‚Ėą‚ēĒ‚ēź‚ēź‚ēź‚ēź‚ēĚ‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚ēĒ‚ēź‚ēź‚ēź‚ēź‚ēĚ ‚Ėą‚Ėą‚ēĎ   ‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚ēĒ‚ēź‚ēź‚Ėą‚Ėą‚ēó‚Ėą‚Ėą‚ēĒ‚ēź‚ēź‚ēź‚ēź‚ēĚ    ‚Ėą‚Ėą‚ēĎ  ‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚ēĒ‚ēź‚ēź‚ēź‚ēź‚ēĚ
‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēó  ‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚ēĎ  ‚Ėą‚Ėą‚Ėą‚ēó‚Ėą‚Ėą‚ēĎ   ‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēĒ‚ēĚ‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēó      ‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēó  
‚Ėą‚Ėą‚ēĒ‚ēź‚ēź‚ēĚ  ‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚ēĎ   ‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚ēĎ   ‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚ēĒ‚ēź‚ēź‚Ėą‚Ėą‚ēó‚Ėą‚Ėą‚ēĒ‚ēź‚ēź‚ēĚ      ‚ēö‚ēź‚ēź‚ēź‚ēź‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚ēĒ‚ēź‚ēź‚ēĚ  
‚Ėą‚Ėą‚ēĎ     ‚Ėą‚Ėą‚ēĎ‚ēö‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēĒ‚ēĚ‚ēö‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēĒ‚ēĚ‚Ėą‚Ėą‚ēĎ  ‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēó         ‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚ēĎ     
‚ēö‚ēź‚ēĚ     ‚ēö‚ēź‚ēĚ ‚ēö‚ēź‚ēź‚ēź‚ēź‚ēź‚ēĚ  ‚ēö‚ēź‚ēź‚ēź‚ēź‚ēź‚ēĚ ‚ēö‚ēź‚ēĚ  ‚ēö‚ēź‚ēĚ‚ēö‚ēź‚ēź‚ēź‚ēź‚ēź‚ēź‚ēĚ         ‚ēö‚ēź‚ēĚ‚ēö‚ēź‚ēĚ     
                                                                 
# Load R libraries
```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  ggplot2,
  scales,
  dplyr,
  stringr,
  ggrepel
)
```

# Prepare environment
```{bash, engine.opts='-l'}
######################################################################################

# Summary:
##########################################################################################
## Calculate support, number of isoforms per gene and loci per each dataset.

##########################################################################################

##########################################################################################
# Remove files from previous run
##########################################################################################
rm -r .temp

##########################################################################################
# Handle errors
##########################################################################################
set -e          # exit on any non-0 exit status
set -o pipefail # exit on any non-0 exit status in pipe

##########################################################################################
# Create directory tree
##########################################################################################
mkdir -p .temp/
mkdir -p .temp/samples/

##########################################################################################
# Move to working directory
##########################################################################################
cd .temp/

##########################################################################################
# Download data
##########################################################################################
# Ensembl.v104 annotation
wget --no-verbose "https://ftp.ensembl.org/pub/release-104/gtf/danio_rerio/Danio_rerio.GRCz11.104.chr.gtf.gz"
# Danio Rerio chromosome sizes
wget --no-verbose "https://hgdownload.soe.ucsc.edu/goldenPath/danRer11/bigZips/danRer11.chrom.sizes"

##########################################################################################
# Set paths
##########################################################################################
utils=../../../Utils/
daniocode_polyA=../../polyA-sites/danRer11_polyAsites.bed.gz
cage=../../CAGE/danRer11_CAGE.bed.gz
chromSizes=danRer11.chrom.sizes
# Annotations
Ensemblv104=Danio_rerio.GRCz11.104.chr.gtf.gz
CapTrap_seq_tmerged=../../Tmerged/output/CapTrap-seq_tmerged.gtf.gz
ZTA_TE_tmerged=../../Tmerged/output/ZTA-TE_tmerged.gtf.gz
ZGA_tmerged=../../Tmerged/output/ZGA_tmerged.gtf.gz
EmbryoFL_tmerged=../../Tmerged/output/EmbryoFL_tmerged.gtf.gz
SuperSet_tmerged=../../Tmerged/output/SuperSet_tmerged.gtf.gz
set3E_tmerged=../../Tmerged/output/3E-set_tmerged.gtf.gz

##########################################################################################
# Copy files
##########################################################################################

##########################################################################################
# Unify chromosomes, exclude patches
##########################################################################################
echo "++++++ Unifying chromosomes and excluding patches ++++++"
echo "@ Processing additional files"
########### Daniocode polyA
zcat $daniocode_polyA | sed 's/^chrM/MT/g' | sed 's/^chr//g' | awk '$1 ~ /^[0-9XYMT]{1,2}$/ {print $0}' > daniocode_polyA.bed
########## Cage
zcat $cage | sed 's/^chrM/MT/g' | sed 's/^chr//g' | awk '$1 ~ /^[0-9XYMT]{1,2}$/ {print $0}' > cage.bed
########## Chrom.sizes
cat $chromSizes | sed 's/^chrM/MT/g' | sed 's/^chr//g' | awk '$1 ~ /^[0-9XYMT]{1,2}$/ {print $0}' > chrom.sizes
########## Ensembl.v104
zcat $Ensemblv104 | sed 's/^chrM/MT/g' | sed 's/^chr//g' | awk '$1 ~ /^[0-9XYMT]{1,2}$/ {print $0}' | awk '$3=="exon"'| gzip -9 > ensembl104.gtf.gz
echo "@ Processing tmerged datasets"
########## Tmerged ZTA-TE # filtering out patches is necessary
zcat $ZTA_TE_tmerged | sed 's/^chrM/MT/g' | sed 's/^chr//g' | awk '$1 ~ /^[0-9XYMT]{1,2}$/ {print $0}' | awk '$3=="exon"'| gzip -9 > ZTA_TE_tmerged.gtf.gz
########## Tmerged ZGA
zcat $ZGA_tmerged | sed 's/^chrM/MT/g' | sed 's/^chr//g' | awk '$1 ~ /^[0-9XYMT]{1,2}$/ {print $0}' | awk '$3=="exon"'| gzip -9 > ZGA_tmerged.gtf.gz
########## Tmerged EmbryoFL
zcat $EmbryoFL_tmerged | sed 's/^chrM/MT/g' | sed 's/^chr//g' | awk '$1 ~ /^[0-9XYMT]{1,2}$/ {print $0}' | awk '$3=="exon"'| gzip -9 > EmbryoFL_tmerged.gtf.gz
########## Tmerged CapTrap-seq
zcat $CapTrap_seq_tmerged | sed 's/^chrM/MT/g' | sed 's/^chr//g' | awk '$1 ~ /^[0-9XYMT]{1,2}$/ {print $0}' | awk '$3=="exon"'| gzip -9 > CapTrap_seq_tmerged.gtf.gz
########## Tmerged SuperSet
zcat $SuperSet_tmerged | sed 's/^chrM/MT/g' | sed 's/^chr//g' | awk '$1 ~ /^[0-9XYMT]{1,2}$/ {print $0}' | awk '$3=="exon"'| gzip -9 > SuperSet_tmerged.gtf.gz
########## Tmerged 3E-set
zcat $set3E_tmerged | sed 's/^chrM/MT/g' | sed 's/^chr//g' | awk '$1 ~ /^[0-9XYMT]{1,2}$/ {print $0}' | awk '$3=="exon"'| gzip -9 > 3Eset_tmerged.gtf.gz
echo ">> DONE"

##########################################################################################
# Build loci for Ensembl and tmerged datasets
##########################################################################################
echo '++++++ Building loci ++++++'
for file in ensembl104 ZTA_TE_tmerged ZGA_tmerged EmbryoFL_tmerged CapTrap_seq_tmerged SuperSet_tmerged 3Eset_tmerged
  do
    echo "Building loci: $file"
    bedtools intersect -s -wao -a $file.gtf.gz -b $file.gtf.gz | $utils/buildLoci.pl - | $utils/gff2gff.pl - | sort -k1,1 -k4,4n -k5,5n | grep '\S' | gzip -9 > samples/$file.loci.gtf.gz
  done
echo ">> DONE"

##########################################################################################
# Get list of samples
##########################################################################################
echo '++++++ Generating the list of samples ++++++'
for file in samples/*loci.gtf.gz
  do
    echo $file >> samples.tsv
  done
echo '>> Done <<'

##########################################################################################
# Extract ends
##########################################################################################
echo '++++++ Extracting ends ++++++'
for file in `cat samples.tsv`
  do
    # Convert to bed
    sample=`basename --suffix .loci.gtf.gz $file`
    echo "Processing $sample"
    zcat $file | $utils/sortgff - | $utils/gff2bed_full.pl - | gzip -9 > samples/${sample}.bed.gz
    for end in 3 5
      do
        zcat samples/${sample}.bed.gz | $utils/extractTranscriptEndsFromBed12.pl $end | sort | uniq | grep '\S' > ${sample}.$end.bed
      done
  done
echo '>> Done <<'

##########################################################################################
# Extract polyA supported transcripts
##########################################################################################
echo '++++++ Looking for polyA supported TM ++++++'
## Extract supported transcripts
for file in `cat samples.tsv`
  do
    sample=`basename --suffix .loci.gtf.gz $file`
    echo "Processing $sample"
    cat ${sample}.3.bed | $utils/sortbed - | bedtools slop -s -l 5 -r 5 -i stdin -g chrom.sizes | bedtools intersect -u -s -a stdin -b daniocode_polyA.bed | grep '\S' > ${sample}.3.vspolyAsignals_DANIOCODE.tsv
  done
echo '>> Done <<'

##########################################################################################
# Extract CAGE supported transcripts
##########################################################################################
echo '++++++ Looking for CAGE supported TM ++++++'
## Extract supported transcripts
for file in `cat samples.tsv`
  do
    sample=`basename --suffix .loci.gtf.gz $file`
    echo "Processing $sample"
    cat ${sample}.5.bed | $utils/sortbed - | bedtools slop -s -l 50 -r 50 -i stdin -g chrom.sizes | bedtools intersect -u -s -a stdin -b cage.bed | grep '\S' > ${sample}.5.vsCage.tsv
  done
echo '>> Done <<'

##########################################################################################
# Extract Cage and polyA supported transcript IDs
##########################################################################################
echo '++++++ Extracting CAGE and polyA supported transcripts ++++++'
for file in `cat samples.tsv`
  do
    sample=`basename --suffix .loci.gtf.gz $file`
    echo "Processing $sample"
    # polyA-supported
    cat ${sample}.3.vspolyAsignals_DANIOCODE.tsv | cut -f4 | sed 's/,/\n/g' | sort | uniq | grep '\S' > ${sample}_DANIOCODE.tx.polyA
    # CAGE-supported
    cat ${sample}.5.vsCage.tsv | cut -f4 | sed 's/,/\n/g' | sort | uniq | grep '\S' > ${sample}.tx.cage
  done
echo '>> Done <<'

##########################################################################################
# Extract Full-length transcript IDs
##########################################################################################
echo '++++++ Extracting Full-length transcript IDs ++++++'
for file in `cat samples.tsv`
  do
    sample=`basename --suffix .loci.gtf.gz $file`
    echo "Processing $sample"
    # polyA-supported
    cat ${sample}_DANIOCODE.tx.polyA | grep -Fwf ${sample}.tx.cage > ${sample}_DANIOCODE.FL.tms.ids
  done
echo '>> Done <<'

##########################################################################################
# Generate data for Barbie plot
##########################################################################################
echo '++++++ Generating data for barbie plot ++++++'
# Remove old plot input
: > ../Figure_4F_plot_input.tsv
for file in `cat samples.tsv`
  do
    sample=`basename --suffix .loci.gtf.gz $file`
    echo "Processing $sample"
    fl=`cat ${sample}_DANIOCODE.FL.tms.ids | wc -l`
    total=`zcat samples/${sample}.bed.gz | cut -f4 | sort | uniq | wc -l`
    propFl=`echo $fl / $total | bc -l`
    gene=`zcat $file | $utils/extract.gtf.tags.sh - gene_id | sort | uniq | wc -l`
    nbTx=`echo $total / $gene | bc -l`
    echo -e "$sample\t$propFl\t$gene\t$nbTx" >> ../Figure_4F_plot_input.tsv
  done
echo '>> Done <<'
  
##########################################################################################
# REPORT COMPLETENESS
##########################################################################################
echo '################## COMPLETED ##################'
```

# Rename catalogs here
```{r}
# Clean the env
rm(list = ls())

df_figure_4f <- read.table("Figure_4F_plot_input.tsv", header = F, as.is = T, sep = "\t") %>%
  rename(
    name = "V1",
    fl = "V2",
    gene = "V3",
    isoforms = "V4"
  ) %>% 
  mutate(type = ifelse(str_detect(name, "tmerge"), "tmerged" , "raw")) %>% 
  # Rename datasets
  mutate(dataset = name) %>%
  mutate(dataset = ifelse(dataset == "ensembl104", "Ensembl v104 (raw)", dataset)) %>%
  mutate(dataset = ifelse(dataset == "ZTA_TE_tmerged", "ZTA-TE (tmerged)", dataset)) %>%
  mutate(dataset = ifelse(dataset == "ZGA_tmerged", "ZGA (tmerged)", dataset)) %>%
  mutate(dataset = ifelse(dataset == "EmbryoFL_tmerged", "EmbryoFL (tmerged)", dataset)) %>%
  mutate(dataset = ifelse(dataset == "CapTrap_seq_tmerged", "CapTrap-seq (tmerged)", dataset)) %>%
  mutate(dataset = ifelse(dataset == "SuperSet_tmerged", "SuperSet (tmerged)", dataset)) %>%
  mutate(dataset = ifelse(dataset == "3Eset_tmerged", "3E-set (tmerged)", dataset))

# Preview
df_figure_4f
```

# Barbie plot - tmerged
```{r}
cbPalette <- c("#cccccc", # ensembl
               "#90e0ef", "#90e0ef", "#90e0ef", # datasets
               "#a0d9d9", # captrap
               "#36caf8", "#8b8bc3") # 3E and superset

df_figure_4f %>% 
  filter(type == "tmerged" | type == "raw") %>% 
  ggplot(data=., aes(x=gene, y=fl, size=isoforms, fill=factor(dataset,
                                                              levels=c("Ensembl v104 (raw)",
                                                                       "ZTA-TE (tmerged)",
                                                                       "ZGA (tmerged)",
                                                                       "EmbryoFL (tmerged)",
                                                                       "CapTrap-seq (tmerged)",
                                                                       "3E-set (tmerged)",
                                                                       "SuperSet (tmerged)"
                                                                       )))) +
  geom_point(shape = 21, alpha = 0.75) +
  geom_label_repel(aes(label = dataset),
                   box.padding   = 0.35,
                   size = 4, 
                   point.padding = 0.5,
                   segment.color = 'grey50') +
  ylab("% Support") +
  scale_fill_manual(values = cbPalette)+ theme_bw(base_size = 24) +
  xlab("Number of loci") +
  #ggtitle("") +
  scale_x_continuous(lim=c(0,50000), breaks=seq(0,50000, by=10000)) +
  scale_y_continuous(labels=percent, lim=c(0,1.0)) +
  theme(axis.text.x = element_text(vjust=0.5),legend.text = element_text(size=12.5)) +
  theme(axis.line.x = element_line(colour = "black"),
  axis.line.y = element_line(colour = "black"),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  strip.background = element_rect(colour="black",fill="white")) +
  scale_size_area(max_size = 17) +
  guides(fill = guide_legend(override.aes = list(size=6.5),
                             title = "Dataset")) -> figure_4f_tmerged_plot

# Preview plot
figure_4f_tmerged_plot
```

# Save plot and input
```{r}
# Save plot
pdf("../../Plots/Figure_4F.pdf", bg = "white", width = 14, height = 9)
figure_4f_tmerged_plot
```
