‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēó‚Ėą‚Ėą‚ēó ‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēó ‚Ėą‚Ėą‚ēó   ‚Ėą‚Ėą‚ēó‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēó ‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēó    ‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēó ‚Ėą‚Ėą‚ēó‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēó 
‚Ėą‚Ėą‚ēĒ‚ēź‚ēź‚ēź‚ēź‚ēĚ‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚ēĒ‚ēź‚ēź‚ēź‚ēź‚ēĚ ‚Ėą‚Ėą‚ēĎ   ‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚ēĒ‚ēź‚ēź‚Ėą‚Ėą‚ēó‚Ėą‚Ėą‚ēĒ‚ēź‚ēź‚ēź‚ēź‚ēĚ    ‚Ėą‚Ėą‚ēĒ‚ēź‚ēź‚ēź‚ēź‚ēĚ‚Ėą‚Ėą‚Ėą‚ēĎ‚ēö‚ēź‚ēź‚ēź‚ēź‚Ėą‚Ėą‚ēó
‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēó  ‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚ēĎ  ‚Ėą‚Ėą‚Ėą‚ēó‚Ėą‚Ėą‚ēĎ   ‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēĒ‚ēĚ‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēó      ‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēó‚ēö‚Ėą‚Ėą‚ēĎ ‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēĒ‚ēĚ
‚Ėą‚Ėą‚ēĒ‚ēź‚ēź‚ēĚ  ‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚ēĎ   ‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚ēĎ   ‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚ēĒ‚ēź‚ēź‚Ėą‚Ėą‚ēó‚Ėą‚Ėą‚ēĒ‚ēź‚ēź‚ēĚ      ‚ēö‚ēź‚ēź‚ēź‚ēź‚Ėą‚Ėą‚ēĎ ‚Ėą‚Ėą‚ēĎ ‚ēö‚ēź‚ēź‚ēź‚Ėą‚Ėą‚ēó
‚Ėą‚Ėą‚ēĎ     ‚Ėą‚Ėą‚ēĎ‚ēö‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēĒ‚ēĚ‚ēö‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēĒ‚ēĚ‚Ėą‚Ėą‚ēĎ  ‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēó    ‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēĎ ‚Ėą‚Ėą‚ēĎ‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚Ėą‚ēĒ‚ēĚ
‚ēö‚ēź‚ēĚ     ‚ēö‚ēź‚ēĚ ‚ēö‚ēź‚ēź‚ēź‚ēź‚ēź‚ēĚ  ‚ēö‚ēź‚ēź‚ēź‚ēź‚ēź‚ēĚ ‚ēö‚ēź‚ēĚ  ‚ēö‚ēź‚ēĚ‚ēö‚ēź‚ēź‚ēź‚ēź‚ēź‚ēź‚ēĚ    ‚ēö‚ēź‚ēź‚ēź‚ēź‚ēź‚ēź‚ēĚ ‚ēö‚ēź‚ēĚ‚ēö‚ēź‚ēź‚ēź‚ēź‚ēź‚ēĚ 
                                                                     
# Load libraries
```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(ggplot2,
               dplyr,
               tidyr,
               ggh4x,
               stringr,
               scales)
```

# Analyse data
```{r}
# Clean the env
rm(list = ls())

#####################################################################
### Load and transform data
#####################################################################

############################### CapTrap_seq
read.table("completeness_output/CapTrap_seq-all.cagePolyASupport.stats.tsv", header = F, as.is = T, sep = "\t") %>%
  select(V1, V5, V6) %>% 
  rename("sample" = "V1") %>% 
  rename("category" = "V5") %>% 
  rename("count" = "V6") %>% 
  mutate(status = "all") %>% 
  bind_rows(read.table("completeness_output/CapTrap_seq-spliced.cagePolyASupport.stats.tsv", header = F, as.is = T, sep = "\t") %>%
              select(V1, V5, V6) %>% 
              rename("sample" = "V1") %>% 
              rename("category" = "V5") %>% 
              rename("count" = "V6") %>% 
              mutate(status = "spliced")) %>% 
  mutate(sample = str_remove(sample, "Pre_0\\+_")) %>% 
  pivot_wider(names_from = "status",
              values_from = "count") %>% 
  mutate(unspliced = all-spliced) %>% 
  pivot_longer(cols = c("all", "spliced", "unspliced"),
               names_to = "splice_status",
               values_to = "count") %>% 
  group_by(sample) %>% 
  mutate(total = sum(count) / 2) %>%  # hehe
  ungroup() %>% 
  mutate(percentage = count / total) %>% 
  # rename for consistency 5'- complete only 5'+3' - complete 3'- complete only 5'+3'- incomplete
  mutate(category = ifelse(category=="cageOnly", "5'- complete only", category)) %>% 
  mutate(category = ifelse(category=="cageAndPolyA", "5'+3' - complete", category)) %>% 
  mutate(category = ifelse(category=="polyAOnly", "3'- complete only", category)) %>% 
  mutate(category = ifelse(category=="noCageNoPolyA", "5'+3'- incomplete", category)) %>% 
  mutate(sample = ifelse(sample=="Heart", "heart", sample)) %>% 
  mutate(sample = ifelse(sample=="Brain", "brain", sample)) %>% 
  mutate(sample = ifelse(sample=="28hpf", "28hpf", sample)) %>% 
  mutate(sample = ifelse(sample=="2-4Cell", "2-4cell", sample)) %>% 
  mutate(sample = ifelse(sample=="Shield", "shield", sample)) %>% 
  mutate(sample = ifelse(sample=="Testis", "testis", sample)) %>% 
  mutate(dataset = "CapTrap-seq") %>% 
############################### ZTA_TE
  rbind(read.table("completeness_output/ZTA_TE-all.cagePolyASupport.stats.tsv", header = F, as.is = T, sep = "\t") %>%
          select(V1, V5, V6) %>% 
          rename("sample" = "V1") %>% 
          rename("category" = "V5") %>% 
          rename("count" = "V6") %>% 
          mutate(status = "all") %>% 
          bind_rows(read.table("completeness_output/ZTA_TE-spliced.cagePolyASupport.stats.tsv", header = F, as.is = T, sep = "\t") %>%
                      select(V1, V5, V6) %>% 
                      rename("sample" = "V1") %>% 
                      rename("category" = "V5") %>% 
                      rename("count" = "V6") %>% 
                      mutate(status = "spliced")) %>% 
          mutate(sample = str_remove(sample, "Pre_0\\+_")) %>% 
          pivot_wider(names_from = "status",
                      values_from = "count") %>% 
          mutate(unspliced = all-spliced) %>% 
          pivot_longer(cols = c("all", "spliced", "unspliced"),
                       names_to = "splice_status",
                       values_to = "count") %>% 
          group_by(sample) %>% 
          mutate(total = sum(count) / 2) %>%  # hehe
          ungroup() %>% 
          mutate(percentage = count / total) %>% 
          # rename for consistency 5'- complete only 5'+3' - complete 3'- complete only 5'+3'- incomplete
          mutate(category = ifelse(category=="cageOnly", "5'- complete only", category)) %>% 
          mutate(category = ifelse(category=="cageAndPolyA", "5'+3' - complete", category)) %>% 
          mutate(category = ifelse(category=="polyAOnly", "3'- complete only", category)) %>% 
          mutate(category = ifelse(category=="noCageNoPolyA", "5'+3'- incomplete", category)) %>% 
          mutate(sample = ifelse(sample=="1cell", "1-cell", sample)) %>% 
          mutate(sample = ifelse(sample=="64cell", "64-cell", sample)) %>%
          mutate(sample = ifelse(sample=="1kcell", "1k-cell", sample)) %>% 
          mutate(sample = ifelse(sample=="30epiboly", "30-epiboly", sample)) %>% 
          mutate(sample = ifelse(sample=="50epiboly", "50-epiboly", sample)) %>% 
          mutate(dataset = "ZTA-TE")) %>% 
############################### ZGA
  rbind(read.table("completeness_output/ZGA-all.cagePolyASupport.stats.tsv", header = F, as.is = T, sep = "\t") %>%
          select(V1, V5, V6) %>% 
          rename("sample" = "V1") %>% 
          rename("category" = "V5") %>% 
          rename("count" = "V6") %>% 
          mutate(status = "all") %>% 
          bind_rows(read.table("completeness_output/ZGA-spliced.cagePolyASupport.stats.tsv", header = F, as.is = T, sep = "\t") %>%
                      select(V1, V5, V6) %>% 
                      rename("sample" = "V1") %>% 
                      rename("category" = "V5") %>% 
                      rename("count" = "V6") %>% 
                      mutate(status = "spliced")) %>% 
          mutate(sample = str_remove(sample, "Pre_0\\+_")) %>% 
          pivot_wider(names_from = "status",
                      values_from = "count") %>% 
          mutate(unspliced = all-spliced) %>% 
          pivot_longer(cols = c("all", "spliced", "unspliced"),
                       names_to = "splice_status",
                       values_to = "count") %>% 
          group_by(sample) %>% 
          mutate(total = sum(count) / 2) %>%  # hehe
          ungroup() %>% 
          mutate(percentage = count / total) %>% 
          # rename for consistency 5'- complete only 5'+3' - complete 3'- complete only 5'+3'- incomplete
          mutate(category = ifelse(category=="cageOnly", "5'- complete only", category)) %>% 
          mutate(category = ifelse(category=="cageAndPolyA", "5'+3' - complete", category)) %>% 
          mutate(category = ifelse(category=="polyAOnly", "3'- complete only", category)) %>% 
          mutate(category = ifelse(category=="noCageNoPolyA", "5'+3'- incomplete", category)) %>% 
          mutate(dataset = "ZGA")) %>% 
############################### EmbryoFL
  rbind(read.table("completeness_output/EmbryoFL-all.cagePolyASupport.stats.tsv", header = F, as.is = T, sep = "\t") %>%
          select(V1, V5, V6) %>% 
          rename("sample" = "V1") %>% 
          rename("category" = "V5") %>% 
          rename("count" = "V6") %>% 
          mutate(status = "all") %>% 
          bind_rows(read.table("completeness_output/EmbryoFL-spliced.cagePolyASupport.stats.tsv", header = F, as.is = T, sep = "\t") %>%
                      select(V1, V5, V6) %>% 
                      rename("sample" = "V1") %>% 
                      rename("category" = "V5") %>% 
                      rename("count" = "V6") %>% 
                      mutate(status = "spliced")) %>% 
          mutate(sample = str_remove(sample, "Pre_0\\+_")) %>% 
          pivot_wider(names_from = "status",
                      values_from = "count") %>% 
          mutate(unspliced = all-spliced) %>% 
          pivot_longer(cols = c("all", "spliced", "unspliced"),
                       names_to = "splice_status",
                       values_to = "count") %>% 
          group_by(sample) %>% 
          mutate(total = sum(count) / 2) %>%  # hehe
          ungroup() %>% 
          mutate(percentage = count / total) %>% 
          # rename for consistency 5'- complete only 5'+3' - complete 3'- complete only 5'+3'- incomplete
          mutate(category = ifelse(category=="cageOnly", "5'- complete only", category)) %>% 
          mutate(category = ifelse(category=="cageAndPolyA", "5'+3' - complete", category)) %>% 
          mutate(category = ifelse(category=="polyAOnly", "3'- complete only", category)) %>% 
          mutate(category = ifelse(category=="noCageNoPolyA", "5'+3'- incomplete", category)) %>% 
          mutate(dataset = "EmbryoFL")) -> df_joined 

# Set levels
dataset_levels <- c("CapTrap-seq", "EmbryoFL", "ZTA-TE", "ZGA")

sample_levels <- c(
  "fertilizedegg", "unfertilized", "1-cell", "2-cell", "64-cell",
  "128-cell", "1k-cell", "high", "oblong", "sphere", "dome",
  "30-epiboly", "50-epiboly", "2-4cell", "shield",
  "28hpf", "brain", "heart", "testis", "75-epiboly", "1-4somites",
  "14-19somites", "20-25somites", "prim-5", "prim-15",
  "prim-25", "long-pec", "protruding-mouth", "day4",
  "day5", "day6", "preZGA", "postZGA"
)

# Apply levels to dataframe
df_joined %>% 
  mutate(dataset = factor(dataset, levels = dataset_levels),
         sample  = factor(sample,  levels = sample_levels)) %>% 
  mutate(facet_var = interaction(dataset, sample, sep = " | ", lex.order = TRUE)) -> df_joined

# Calculate percentage for each bar for each sample
df_joined %>% 
  group_by(facet_var, splice_status) %>% 
  summarise(percent_per_bar = sum(percentage)) %>% 
  ungroup() -> df_percent_helper

# Preview dataframe
df_joined
df_percent_helper
```  
  
# Plot data
```{r}
# Plot data
df_joined %>% 
  ggplot(data=.,
         aes(x=splice_status, y=percentage)) +
  geom_bar(stat="identity",
           aes(fill=factor(category, levels = c("5'- complete only",
                                                "5'+3' - complete",
                                                "3'- complete only",
                                                "5'+3'- incomplete"))))  +
  geom_text(aes(label = ifelse(count > 0, paste0(scales::percent(percentage, accuracy = 0.1),"\n", "(", comma(count), ")"), ""),
                fill=factor(category, levels = c("5'- complete only",
                                                "5'+3' - complete",
                                                "3'- complete only",
                                                "5'+3'- incomplete"))),
            position = position_stack(vjust = 0.5),
            size=1.5) +
  geom_text(data = df_percent_helper,
            aes(x = splice_status,
                y = 1.05,
                label = scales::percent(percent_per_bar, accuracy = 0.1)),
            vjust = -0.5,
            size = 1.8,
            color = "blue") +
  scale_y_continuous(limits=c(0, 1.1), labels=percent) +
  ylab("Percent of Transcript Models") +
  theme_bw() +
  ggtitle("") +
  scale_fill_manual(values=c("#e5b3e5","#C453C4","#b3e0ff","#a6a6a6")) +
  xlab("") +
  theme(axis.text.x = element_text(size = 5, colour = "black", vjust=0.5),
        axis.text.y = element_text(size = 8,  colour = "black"),
        legend.text = element_text(size = 8, hjust=0.5),
        plot.title = element_text(size = 22),
        legend.title = element_text(size=0, color="white"),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        strip.text.x=element_text(size=7),
        strip.text.y=element_text(size=10)) +
  theme(legend.position="top") +
  facet_wrap(~ facet_var,
             labeller = labeller(facet_var = function(x) gsub(" \\| ", "\n", x)),
             scales="free_x",
             ncol=8) -> Figure_S13

# Preview plots
Figure_S13
```

## Save plot
```{r}
# Save plot
pdf("../../Plots/Figure_S13.pdf", bg = "white", width = 8, height = 11)
Figure_S13
```
